### 2018-04-29 paper/abstract.tex
Fixes blank line bug in abstract
pass on abstract. Tightening up. Also reformatted authors to take less space.

% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

%abstract
%problem/topic
This paper presents privacy-preserving file sharing without relying on any third-party storage such as cloud services or peers.

%research gap
Centralized file-sharing systems, i.e. cloud storage such as Dropbox require trust in the service provider and can be monitored. P2P file-sharing relies on replicas on other people's machines. We are interested in minimizing trust needed in other systems and preserving the user's privacy in terms of data and metadata, i.e. what they share with whom and when.

%why now
Nowadays, many people use multiple devices and it has thus become possible to benefit from p2p technology for one's own devices alone and thus reducing one's exposure to security and privacy vulnerabilities and threats from third parties.

%approach
We enable onion routing to cope with probabilistic availability of nodes, informed by peer sampling and Hidden Markov Model predictions.

%findings/contributions:
We benefit from sender-receiver anonymity properties provided by onion routing. We show that even a relatively naive prediction model suffices to share files despite unreliable availability of individual nodes. The same model can potentially be applied for better informed churn handling in other p2p systems. In the case of TOR-like onion routing systems for anonymity, our solution allows the system to include unreliable nodes and take advantage of locality.

>>>>

% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?
%
%abstract
%problem/topic
This paper proposes a novel fully-decentralized privacy-preserving file sharing service that eschews any third-party storage or any centralized bootstrapping service.
%research gap
Cloud-based file-sharing systems such as Dropbox require trust in the service provider and can be monitored, even when their data is encrypted. Private peer-to-peer (P2P) solutions are either particularly inefficient, or must rely on a fixed set of trusted servers for bootstrapping purposes, which limit their level of protection. % We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
%why now
% Nowadays, many people use multiple devices and it has thus become possible to benefit from P2P technology for one's own devices alone, thereby reducing one's exposure to security and privacy threats from third parties.
%approach
In this paper, we demonstrate that an efficient and strongly private fully-decentralized data-sharing solution is possible. Our proposal combines onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
%findings/contributions:
Our solution benefits from sender-receiver anonymity properties provided by onion routing. %% to protect user privacy in decentralized file sharing.
We show that even a relatively naive prediction model suffices to share files despite the unreliable availability of individual nodes. %% The same model can potentially be applied for better-informed churn handling in other p2p systems. In the case of onion routing systems for anonymity, 
Our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.

### 2018-04-29 paper/intro.tex
pass on abstract. Tightening up. Also reformatted authors to take less space.

% What's the problem?
Following Mark Weiser's vision, we are nowadays
experiencing a new era of cooperation and interactions between humans.
The exponential proliferation of connected devices is
drastically impacting human experience and enhancing human
exchanges~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. This evolution has opened new areas of research such as
\textit{proxemics} applied to ubiquitous computing
\cite{Marquardt:2011}. When evolving in their social space, users can today rely on
multiple kinds of computing devices that form a \textit{personal squad} of connected entities, or \squad as we shall call them in the remainder of the
paper. Helped by their \squad, users
have come to expect ever higher levels of connectivity and interaction
possibilities. For instance, as users bring
their devices close to one another, they expect to be able to initiate cross-device
interactions \textit{in situ} in order to share digital content
\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad. More broadly, users expect to share digital content,
wherever the content, its sender, or its recipient might be located, from one
arbitrary device to another in a seamless manner~\cite{Dearman:2008}, as they
would have done in the old days with an USB key or with an email.

@@

In this paper, we demonstrate how good performance can be reconciled with strong privacy protection in data-sharing systems. We present \name{}, a novel fully decentralized, autonomous,
% approach that provides a 
and self-organizing file sharing service between the \squad of different users that preserves user privacy
in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
transfers. Close distance among users enable them to share
routing information out-of-band, e.g. from their
\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Second}, we
rely on distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism. The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.

>>>>

% What's the problem?
Following Mark Weiser's vision, we are nowadays
experiencing a new era of cooperation and interactions between humans.
The exponential proliferation of connected devices is
drastically impacting human experience and enhancing human
exchanges~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. This evolution has opened new areas of research such as
\textit{proxemics} applied to ubiquitous computing
\cite{Marquardt:2011}. When evolving in their social space, users can today rely on
multiple kinds of computing devices that form a \textit{personal squad} of connected entities, or \squad as we shall call them in the remainder of the
paper. Helped by their \squad, users
have come to expect ever higher levels of connectivity and interaction
possibilities. For instance, as users bring
their devices close to one another, they expect to be able to initiate cross-device
interactions \textit{in situ} in order to share digital content
\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad{}\emph{s}. More broadly, users expect to share digital content,
wherever the content, its sender, or its recipient might be located, from one
arbitrary device to another in a seamless manner~\cite{Dearman:2008}, as they
would have done in the old days with an USB key or with an email.

@@

In this paper, we demonstrate how good performance can be reconciled with strong privacy protection in data-sharing systems. We present \name{}, a novel fully decentralized, autonomous,
% approach that provides a 
and self-organizing file sharing service between the \squad{}\emph{s} of different users that preserves user privacy
in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
transfers. Close distance among users enable them to share
routing information out-of-band, e.g. from their
\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Second}, we
rely on distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism. The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
